---
title: '2018.09.04: Fast food entree data'
author: "Khadra Mohamed"
date: '2022-04-22'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###library loading

```{r library loading}
library(tidyverse) 
library(scales) 
theme_set(theme_light())
```

### Reading the data

```{r reading the data}
 fastfoodC <-  read.csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2018/2018-09-04/fastfood_calories.csv")
```

### Arranging the data in “calories” descending order

```{r arranging the data in "calories "descending order}
data_processed <- fastfoodC %>%   arrange(desc(calories))
```

### Data overview

```{r Data overview}
data_processed %>%   ggplot(aes(calories)) +   geom_histogram()
```

### The 30 food items with the highest calories

```{r 30 food items with the highest calories}
data_processed %>%   
  mutate(item = fct_reorder(item, calories)) %>%   
  head(30) %>%   
  ggplot(aes(item, calories)) +   
  geom_col() +   
  coord_flip()
```

### The 30 food items with the lowest calories

```{r 30 food items with the lowest calories }
data_processed %>%   
  mutate(item = fct_reorder(item, calories)) %>%   
  tail(30) %>%   
  ggplot(aes(item, calories)) +   
  geom_col() +
  coord_flip()
```

### Which restaurants sell food items with the highes calories?

```{r which resturants sell food items with high calories?}
 data_processed %>%   
  mutate(item = fct_reorder(item, calories)) %>%   
  head(30) %>%   
  ggplot(aes(item, calories, fill = restaurant)) +   
  geom_col() +   
  coord_flip()
```

### What are the contents of the food items with the highest calories?

```{r contents of the food items with the highest calories}
data_processed %>%   
  mutate(item = fct_reorder(item, calories)) %>%   
  head(30) %>%
  gather(facts, number, sugar, protein, fiber, total_carb) %>%
  mutate(item= fct_reorder(item, number)) %>%
  ggplot(aes(item, number, fill = facts)) +
  geom_col() +
  coord_flip()
```

### Which restaurants sell food items with the lowest calories?

```{r which resturants sell food items with low calories? }
data_processed %>%
  mutate(item = fct_reorder(item, calories)) %>%
  tail(30) %>%
  ggplot(aes(item, calories, fill = restaurant)) +
  geom_col() +
  coord_flip()
```

### What are the contents of the food items with the lowest calories?

```{r contents of the food items with the lowest calories }
data_processed %>%
  mutate(item = fct_reorder(item, calories)) %>%
  tail(30) %>%
  gather(facts, number, sugar, protein, fiber, total_carb) %>%   mutate(item= fct_reorder(item, number)) %>%
  ggplot(aes(item, number, fill = facts)) +
  geom_col() +
  coord_flip()
```

### What is the correlation between high calories and cholestrol?

```{r correlation between high calories and cholestrol}
data_processed %>%
  ggplot(aes(calories, cholesterol)) +
  geom_smooth(aes(method = "lm")) +
  geom_point()
```

